NumPy---Array Programming in Python

### 2020-01-31 body.tex
Strengthen final paragraph; still needs editing

Over time the role of the NumPy has evolved.
It began as an attempt to add an array object to Python
and became the foundation of a rich ecosystem of tools.
Now a large amount of scientific work depends on NumPy
being correct, fast, and stable.
Yet, it is no longer just the foundational array library underlying the
scientific Python ecosystem; it is also the standard API for tensor
computation and a central coordinating mechanism between array types and
technologies in Python.
NumPy continues to evolve.
For instance, the NumPy data type system is currently being redesigned to make it
easier to implement data types both in Python and C, and to better handle
richer data types including physical units \cite{astropy,Goldbaum2018,pint},
geometrical objects \cite{pygeos}, and missing values.
% Maybe add a sentence in the direction of:
% We hope/expect, that this will allow the proliferation of rich datatypes
% which in turn can propel the whole ecosystem forward? (too much :)?
% As a part of other changes/developements...)
% Discussed with Jarrod, if it fits to get back to protocols, it is fine
% to call DTypes a (rich) protocol.

>>>>

NumPy began as an attempt to add an array object to Python and became
the foundation of a rich ecosystem of tools.
Now, a large amount of scientific work depends on NumPy being correct,
fast, and stable.
Work on NumPy continues, so that it may meet the needs of its users.  For instance, the NumPy data type system is currently being redesigned to make it
easier to implement data types both in Python and C, and to better handle
rich data types such as physical units \cite{astropy,Goldbaum2018,pint},
geometrical objects \cite{pygeos}, and missing values.
% Maybe add a sentence in the direction of:
% We hope/expect, that this will allow the proliferation of rich datatypes
% which in turn can propel the whole ecosystem forward? (too much :)?
% As a part of other changes/developements...)
% Discussed with Jarrod, if it fits to get back to protocols, it is fine
% to call DTypes a (rich) protocol.

NumPy's role in the ecosystem continues to evolve. It is no longer just the foundational array library underlying the
scientific Python ecosystem, but has become the standard API for tensor
computation and a central coordinating mechanism between array types and
technologies in Python.
